---
title: "Farm selection"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

this script contains code to define the farm typology used for the Farm2Forest project. 

For that we link the 

+ blockdata
+ animal data



```{r}
library(sf)
#library(raster)
library(vegan)
library(readr)
library(ggplot2)
library(plotly)
library(readxl)
library(dplyr)
library(tidyr)
library(multidplyr)
library(purrr)
```


**geom_sf (to plot sf woth ggplot) is so far only available in the devellopment version of ggplot. The code below will check if it is available and install the devellopment version of ggplot if not**

```{r, eval = FALSE}
if( "ggplot2" %in% .packages() && exists('geom_sf', mode='function') == FALSE) {
  
  library(devtools)
  devtools::install_github("tidyverse/ggplot2")
  
}

```


## load data

we use the agricultural reference data from 2012 together with the animal data from 2012.
We will use newer versions of both when available (waiting for animal data)

### agricultural reference data 2012 

+ to match the animal data we create a varibale calle `kundnr1` composed of the `lan` and the `kundnr`

```{r, eval = TRUE}
RPD_2012 <- st_read("/Volumes/Fabian_Work/Reference parcel data shapelayers/S_jbb2012.shp") %>% 
  mutate(kundnr1 = paste(lan, kundnr, sep = " "))
head(as.data.frame(RPD_2012))
```

### load shapefile of Sweden

+ we load a shapefile of Sweden with the administrative borders (kncluding the sea)
+ we load a shapefile that define our study regions (by Yann)

```{r}
Sweden <- st_read("/Volumes/Fabian_Work/Lantmateriet/GSD-Sverigekartor_vektor/1_milj/Sverige/Sweref_99_TM/shape/sve_1milj_Sweref_99_TM_shape/svk/riks/ak_riks.shp", stringsAsFactors = FALSE, options = "ENCODING=UTF-8")

F2F_regions <- st_read("Shapes/prod_län_combi_byyann_skarning2.shp", stringsAsFactors = FALSE, options = "ENCODING= UTF-8") %>% 
  mutate(LAN_NAMN = c("Jönköpings län", "Skåne", "Västerbottens län"))

Sweden %>% 
  group_by(LANSNAMN) %>% 
  st_set_precision(100) %>% 
  summarize(unique(LAN_KOD)) %>% 
  ggplot()+
  geom_sf()+
  geom_sf(data = F2F_regions, aes(fill = LAN_NAMN) )
```


### load data about location of Farmsteads 
```{r}
Farmstead <- read_delim("/Volumes/Fabian_Work/Brukare_brukningscentrum_ansi.txt", delim = "\t", locale = locale(encoding = "latin1"))

Farmstead <- filter(Farmstead, `Brukningscentrum JA/NEJ` == "Ja") %>% select(Kundnr, `Block Id`, `Brukningscentrum JA/NEJ`)
```



### subset for study regions

we check for each block whether it intersects with either of the 3 study regions and then filter all kundnr that have at least one block in the study region

because this is a rather time consuming operation we parallelize the code

```{r}
RDP_cl <- RPD_2012

start <- proc.time()

# initialize cluster and create groups (replace cores with number of cores you want to use)
cl <- create_cluster(cores = 4)
group <- rep(1:length(cl), length.out = nrow(RDP_cl))
RDP_cl <- bind_cols(tibble(group), RDP_cl)

RDP_cl <- RDP_cl %>%
    partition(group, cluster = cl)

# make relevant packages and data available to clusters
RDP_cl %>% 
  cluster_library("tidyverse") %>%
  cluster_library("sf") %>% 
  cluster_assign_value("F2F_regions", F2F_regions) 
    
RDP_cl <- 
RDP_cl %>%
  mutate(in_study_region = map(geometry, function(x) st_within(x, F2F_regions$geometry, sparse = F))) %>% 
  collect()  
  

time_elapsed_parallel <- proc.time() - start 


```

we tested for each block if it is in either of the three study regions, resulting in a logical list-column. as the list colum contains a 1 x 3 matrix we first need to transform it to a vector of length 3, and then we can unnest it.

```{r}
RPD_2012_sub <- 
RDP_cl %>% 
  mutate(in_study_region = map(in_study_region, function(x) c(unlist(x)))) %>% 
  unnest(in_study_region, .preserve = geometry) %>% 
  ungroup() %>% 
  mutate(region = rep(F2F_regions$LAN_NAMN, nrow(.)/3)) 


save.image(file = "Subsampled_joined_data_2012.RData")


```


+ subset for all kundnr that have at least one block in either of the study regions

```{r}
Kundr_in_studyRegion <- filter(RPD_2012_sub, in_study_region) %>% 
  select(kundnr1) %>% unique

RPD_2012_sub <- 
  RPD_2012_sub %>%
  filter(kundnr1 %in% Kundr_in_studyRegion$kundnr1)
```

check if any block is assigned to more than one region

```{r}

RPD_2012_sub %>% 
  select(blockid, in_study_region, region) %>% 
  distinct() %>% 
  group_by(blockid) %>% 
  summarise(in_study_region = sum(in_study_region)) %>% 
  filter(in_study_region > 1) 

```

simplify dataset to only have one row per blockid x grodkod/areal combination with a logical colum `in_study_region` and a colum `region` giving the study region or else NA. 

```{r}
Blocks_in_sr <- 
  RPD_2012_sub %>% 
  select(blockid, in_study_region, region) %>% 
  filter(in_study_region) %>% 
  distinct

RPD_2012_sub <- 
RPD_2012_sub %>% 
  select(-in_study_region, -region) %>% 
  distinct() %>% 
  left_join(Blocks_in_sr) %>% 
  mutate(in_study_region = case_when(is.na(in_study_region) ~ FALSE,
                                     TRUE ~ TRUE))

```



+ check what proportion of kundnr have fields outside the study regions
```{r}

Kundr_in_studyRegion <- 
RPD_2012_sub %>% 
  group_by(kundnr1, in_study_region) %>% 
  summarise(area = sum(blockarea)) %>% 
  arrange(kundnr1) %>% 
  mutate(all_in_SR = case_when(FALSE %in% in_study_region ~ "no",
                               ! FALSE %in% in_study_region ~ "yes",)) 

length(unique(Kundr_in_studyRegion[Kundr_in_studyRegion$all_in_SR == "no", ]$kundnr1)) /
  length(unique(Kundr_in_studyRegion$kundnr1)) * 100
```

+ about 10% of the kundr have blocks inside and outside the study regions

For those with blocks both inside and outside the study region, what proportion (by area) is inside the study region?

```{r}
Kundr_notonly_SR <- 
Kundr_in_studyRegion %>% 
  filter(all_in_SR == "no") %>% 
  spread(in_study_region, area) %>% 
  mutate(prct_area_in_SR = `TRUE` / (`TRUE`+`FALSE`)) 

Kundr_notonly_SR %>% 
  ggplot(aes(x = prct_area_in_SR))+
  geom_histogram()+
  geom_vline(xintercept = 0.25, colour = "red", linetype = "dashed")+
  theme_bw()


```

+ we keep all farms with a min of 25% of their landarea in the study regions

```{r}

kundnr_exclude <- Kundr_notonly_SR %>% 
  filter(prct_area_in_SR < 0.25)

RPD_2012_sub <- 
  RPD_2012_sub %>% 
  filter(!kundnr1 %in% kundnr_exclude$kundnr1) 

RPD_2012_sub <- 
Kundr_in_studyRegion %>% 
  spread(in_study_region, area) %>% 
  mutate(prct_area_in_SR = `TRUE` / (`TRUE`+`FALSE`)) %>% 
  select(-`TRUE`, -`FALSE`) %>% 
  mutate(prct_area_in_SR = case_when(all_in_SR == "yes" ~ 1,
                                     all_in_SR == "no" ~ prct_area_in_SR)) %>% 
left_join(RPD_2012_sub, .)
  
  

```

+ export map with selected kundnr

```{r}
RPD_2012_sub <- 

st_write(RPD_2012_sub, "RPD_2012_sub.gpkg", delete_layer = TRUE)
```

