---
title: "R Notebook"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```


```{r}
library(sf)
library(tidyverse)
library(gridExtra)
library(RColorBrewer)
library(readxl)
library(raster)

library(fastmatch)
library(rmapshaper)
```

```{r}
APD_2015 <- st_read("/Volumes/Fabian_Work/Agricultural parcel data/2015.shp")

```
# Data availability

#Agricultural parcel data 2015

proj4string:    +proj=utm +zone=33 +ellps=GRS80 +units=m +no_defs

Shape file with 11 columns:

+ `ID`: unique ID for each Agricultural Parcel (1.222621 Mio) - there can be multiple parcels per block

+ `KUND_LAN`: [Letter code for swedish regions](https://sv.wikipedia.org/wiki/Länsbokstav) 

```{r}
APD_2015 %>% 
  group_by(KUND_LAN) %>% 
  sample_frac(size = 0.01) %>% 
  select(KUND_LAN) %>% 
  plot(., col = .$KUND_LAN, border =.$KUND_LAN )
```

```{r}
CC <- read_csv2("County_codes.csv")

CC
```


+ `KUND_LOPNR`: Customer ID (14983 unique IDs). The one who applies for subsidies
    + Doesn't have to be the one who cultivates it (owner could take subsidies and rent it out afterwards)
    + Doesn't have to be the owner (could rent land) 
    + Large farms can have several costumer numbers (subsidary companies)
    + Sometimes passing the land to younger generation results in two costumer numbers (the heirs might not divide the land but create a holding)


```{r, fig.height=3, fig.width=5}

p1 <- table(APD_2015$KUND_LOPNR) %>% 
  sort(.,decreasing = T) %>% 
  as.data.frame() %>% 
  mutate(rank = 1:nrow(.)) %>% 
  ggplot(aes(x = Freq))+
  geom_histogram()+
  scale_x_log10(breaks = c(1,10,100,1000))+
  theme_bw()+
  labs(title = "distribution of #parcels",
       x= "number of plots / C.ID.")

p2 <- table(APD_2015$KUND_LOPNR) %>% 
  sort(.,decreasing = T) %>% 
  as.data.frame() %>% 
  mutate(rank = 1:nrow(.)) %>% 
  mutate(cumsum = (cumsum(Freq)/sum(Freq))*100) %>% 
  ggplot(aes(x = rank, y = cumsum))+
  geom_point()+
  theme_bw()+
  labs(title = "cumulative %",
       x= "C.ID. rank (largest to smallest)")

grid.arrange(p1,p2, nrow = 1)

```


+ `SAMIBLOCK_` : unique ID for each Reference Parcel (1.068528 Mio)

+ `SKIFTESBET` : ??, 3510 levels, first 200 make up > 90%, ( first 10 make up ~ 30%)

+ `EFATYPE`, 4 levels
    + Kvavefixerade grodor (0.5%)
    + Salix (0.1%)
    + Skiften med insadd av vall (1.26%)
    + Trada (3.3%)
    + NA (94.8%)
  
+ `SAMISKIFTE`: unique ID for each Agricultural Parcel (redundant with ID?)

+ `OBJECTID`: unique ID for each Agricultural Parcel (redundant with ID?)

+ `AREAL`: rounded area in hectar of each Agricultural Parcel (OBS, inconsisting rounding)

+ `OMKRETS`: sum of the perimeters of the polygones defining each  Agricultural Parcel. 
  
+ `MYGRODKOD`: Crop codes, 82 levels
    + 50 (Slåtter och betesvall på åker) - 41.6%
    + 52 (Betesmark (ej åker)) - 16.6%
    + 60 (Träda) - 9.3%
    + 49 (Slåtter och betesvall på åkermark med  en  vallgröda som ej är godkänd för miljöersättning) - 7.4%
    
```{r}

d1 <- table(APD_2015$MYGRODKOD) %>% 
  sort(.,decreasing = T) %>% 
  as.data.frame() %>% 
  mutate(rank = 1:nrow(.)) 

p3 <- d1 %>% 
  ggplot(aes(x = rank, y = Freq))+
  geom_bar(stat = "identity")+
  theme_bw()+
  labs(y = "# of parcels", x = "rank of cropcodes",
       title = "distribution of crop codes")

p4 <- d1 %>% 
  mutate(Freq = signif((Freq / sum(Freq)) * 100, 2)) %>% 
  filter(rank <= 7) %>%
  ggplot(aes(x = rank, y = Freq, fill = Var1))+
  geom_bar(stat = "identity")+
  theme_bw()+
  scale_fill_brewer(palette = "Set1", name = "Cropcode")+
  labs(y = "% agricultural parcels", title = "7 most common cropcodes")
  

grid.arrange(p3,p4, nrow = 1)

```
    

+ `geometry`: Polygones defining the Agricultureal Parcels. Kan have holes
  
## Agricultural parcel data 2016

Same as for 2015

## Agricultural parcel data 2017

+ missing Costumer ID
+ only data for Skåne
+ pre-application data

## List of crop codes

(Grödkodslista+2017+webbexemplar+2017-01-16.xlsx)

+ defines each cropcode (in swedish)
+ bolean variables for subsedies stating whether that cropcode is elegible for that agri-environmental subsedy
+ bolean variables for subsedies stating whether that cropcode was elegible for that subsedy in the timeframe 2007-2013

## List of additional subsidies

Utvald+miljö+2017+webbexemplar+2016-12-09.xlsx

+ bolean variables for subsedies stating whether that cropcode is elegible for that subsedy



#Reference parcel data 2014 (Blockdatabasen)

`r st_crs(RPD_2015)`

database with 7 columns

+ `blockid` unique ID for each reference parcel
    + each block can have several skifte (up to 25 on 1 block??), and different cropcodes
    + `r round((sum(table(RPD_2015$blockid) > 1)/length(unique(RPD_2015$blockid)))*100, 1)` % of blocks have more than 1 skifte
    
+ `lan` [Letter code for swedish regions](https://sv.wikipedia.org/wiki/Länsbokstav) 

+ `kundnr` Customer ID (13896 unique IDs). The one who applies for subsidies
    + Doesn't have to be the one who cultivates it (owner could take subsidies and rent it out afterwards)
    + Doesn't have to be the owner (could rent land) 
    + Large farms can have several costumer numbers (subsidary companies)
    + Sometimes passing the land to younger generation results in two costumer numbers (the heirs might not divide the land but create a holding)

+ `grodkod` the crop codes. 
    + There can be several cropcodes on one block
    + we know how much of each cropcode (area) is in each block but not where

+ `areal` area of each cropcode in each skifte in each block (in ha)

+ `blockarea` area of the block (in ha)

+ `geometry` polygone defining the reference parcel

#SLU forest map (kNN-Svergie)

```{r}
# path to data
path_to_raster <- "/Volumes/Fabian_Work/SLU Forest Map/2010/Data/Raster/Sweref99TM"

#list all layers
files <- list.files(path_to_raster, full.names = T)

#grep .tif files
files <- files[grepl(".tif$", files)]

#load first layer
knnS <- raster(files[1])

#add all layers

for (i in 2:length(files)){
  temp <- raster(files[i])
  knnS <- stack(knnS, temp)
}

```



Forest map for Sweden, based on the [Riksskogstaxeringen](https://www.slu.se/riksskogstaxeringen) (the swedish national forest inventory) and satelite imagery.

+ Rastermap with 25 m^2 resolution
+ based on k-nearest neighbourgh algorithm, matching satelite immagery with the weighted average of closest match from corresponing satelite imagery of known area, from the swedish national forest inventory.

data:

+ Forest age
    